% testing.tex
\chapter{Testing}

\section{Test Strategy}
In this section I will compare my my finished project with the original specification proposed in my Analysis section. Furthermore, I will demonstrate my app as a whole.

Video demonstration of the app will be provided to show the app in action, this will provide a complete overview of the app and its features. This is my acceptance testing as it will show the app in action and how it meets the original requirements.

The primary testing strategy for my backend project would be Unit testing to see if all the smaller components of my app work as intended. Django provide its own testing framework built on top of Python's unittest module. I will be using this to test my models and the methods within them, as well as the utility functions I have created in my app. Normal, boundary and edge cases will be tested where applicable. In addition, screenshots of the PostgreSQL database will also be shown.

For the API endpoints I will be using REST client provided by Visual Studio Code to make HTTP requests to the server and compare the result with my anticipated result. I will be doing this rather than using Django's own testing framework because I want to model real world usage of my app. This is my system testing for the backend as it will test the functionality of the server as a whole.

For my frontend Interface, I will be will be testing the app manually by interacting with the components to see if the app behaves as expected. There will be screenshots of the results of the test cases. 



\subsection{Unit Testing}
To test my backend code django includes its own...

\section{Endpoints}
To model real world usage, I will be making real HTTP requests to the server and compare the result with my anticipated result.


\subsection{Rest Client}
\subsection{Django Test Models}

\section{Testing Video}
Include a link or description of a testing video.

\section{System Tests}
Conduct tests against the original requirements specification.



